---
title: "INFO 3010 - Assignment 6"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## by Lingzi Hong
### Instructions
1. This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button, all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
2. Please download the snowstorm.json from canvas. Fill in the code chunks for following question and submit this R markdown file to the assignment on Canvas. Make sure when you save that you have run all cells, so the outputs displace between the cells.
3. make sure to replace the directoryID in the filename with your student ID. 
4. You can get 5 bonus points for using ggplot2 package.


### Q1. (5pts) Download the 'HousePrice.csv' dataset. Read the dataset to a dataframe. Check the structure of the dataframe.
```{r}
HousePrice_df <- read.csv('C:\\Users\\Sam\\Documents\\INFO3010\\assignment downloads\\HousePrice.csv')

str(HousePrice_df)

```

### Q2. (10pts) Draw a density plot and a histogram to check the distribution of house price. What's the difference between the histogram and density plot?
```{r}
hist(HousePrice_df$Price)
```

### Q3. 1) (5pts) Get a subset of data with postal code as "98178","98146" and "98118".  2) (10pts) Draw a scatter plot with the subset data. It has Sqft_Area in x-axis, Price in y-axis. The dots are colored by postal code.  
```{r}
subset <- HousePrice_df[(HousePrice_df$Postal==98178)|(HousePrice_df$Postal==98146)|(HousePrice_df$Postal==98118),]

library(ggplot2)

x <- ggplot(data = subset)+
  geom_point(mapping = aes(x=Sqft_Area, Price),color = subset$Postal)

x
```


### Q4. (10pts) Randomly choose a dataset you are interested. You may also keep using the hourseprice dataset. Draw a scatter plot matrix. What do you find? Write 2-3 sentences about your finding. Remember to write the sentences outside of code chunk.

```{r}
pairs(~Crime+Price+MedIncome,data=HousePrice_df,lower.panel=panel.smooth)

#

```

### Q5. (10pts) Choose any three variables from Q4 and draw a plot to explore the relations of the three variables. 
```{r}

p <- ggplot(HousePrice_df, aes(x = Crime, y = Sqft_Area , color = Population )) +
  geom_point()
p
```

